Topological Equivariant Artist Model

### 2022-03-28 slides/main.tex
compiles, presentation mode

\documentclass[xcolor={dvipsnames}, handout]{beamer}
%\documentclass[xcolor={dvipsnames}]{beamer}
\setbeamertemplate{footline}[frame number]
\setbeamersize{description width=-\labelsep}

@@

%% maybe pull out the middle for now? move the 3 stages down to construction? 
\begin{frame}<presentation:1|handout:0>{What do visualization libraries do?}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:1>\includegraphics[width=\linewidth]{figures/flow/s2.png}
            \onslide<2|handout:2>\includegraphics[width=\linewidth]{figures/flow/s_vc.png}
            \onslide<3|handout:3>\includegraphics[width=\linewidth]{figures/flow/s_mark.png}
            \onslide<4|handout:4>\includegraphics[width=\linewidth]{figures/flow/s3.png}
        \end{overprint}
    \end{figure}
\end{frame}

@@

\begin{frame}<presentation:1|handout:0>{Equivariance}
    \begin{description}
        \item[Retinal Variables \& Marks] visual encodings should match properties of the data \cite{bertinSemiologyGraphicsDiagrams2011a}
        \pause
        \item[Graphical Integrity] graphs show \textbf{only} the data\cite{tufteVisualDisplayQuantitative2001}
        \pause 
        \item[Naturalness] easier to understand when properties match\cite{norman_things_smart}
        \pause
        \item[Expressiveness] which structure preserving mappings can a tool implement\cite{mackinlayAutomatingDesignGraphical1986}] 
    \end{description}
\end{frame}

%flip columns
\begin{frame}<presentation:1|handout:0>{Frameworks for Expressing Visual Equivariance}
    \begin{description}
        \item[linguistically] visualization has syntax, semantics, grammar expresses how to design structure preserving visualizations
        \cite{mackinlayAutomatingDesignGraphical1986,mackinlayAUTOMATICDESIGNGRAPHICAL1987,wilkinsonGrammarGraphics2005}

        \item[algebraically] transformations on data and graphics are equivalent symmetric \cite{kindlmannAlgebraicProcessVisualization2014}
        \begin{columns}
            \column{.5\textwidth}
            \begin{description}
                \item[D] data 
                \item[R] data representation 
                \item[V] visualization
            \end{description}
            \column{.5\textwidth}
            \begin{equation*}
                \begin{tikzcd}[ampersand replacement=\&]
                    D \arrow[d, "\alpha"'] \arrow[r, "r_1"] \& R \arrow[r, "\nu"]  \& V \arrow[d, "\omega"] \\
                    D \arrow[r, "r_2"']                     \& R \arrow[r, "\nu"'] \& V                    
                \end{tikzcd}
                \end{equation*}
        \end{columns} 
    \item[categorically] \textit{understanding} = \textit{read} $\circ$ \textit{render} \cite{vickersUnderstandingVisualizationFormal2013}    
    \end{description}
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>

@@

    \only<4-5|handout:1>{

@@

\subsection{Category Theory Language}
\begin{frame}<presentation:1|handout:0>[fragile]{}
    \begin{minted}{python}
        Artist(data:Data) -> Graphic
    \end{minted}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \onslide*<1-|handout:1>{\textcolor{source}{C_1}} 
        \onslide*<3-|handout:1>{\arrow[r, "f", color=source]}
        \onslide*<4-|handout:1>{\arrow[rd, "g\circ f"', color=source]}
        \onslide*<2-|handout:1>{\arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source]} \& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_2}}
        \onslide*<3-|handout:1>{\arrow[d, "g", color=source]} 
        \onslide*<2-|handout:1>{\arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]} \\\& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_3}}
        \onslide*<2-|handout:1>{\arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]}              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}<5-|handout:1>{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Opposite Category $\textcolor{source}{\mathcal{C}^{op}}$}
    \begin{columns}
        \column{0.49\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \textcolor{fade}{C_1} \arrow[r, "f", color=fade] \arrow[rd, "g\circ f"', color=fade] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=fade] \& \textcolor{fade}{C_2} \arrow[d, "g", color=fade] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=fade] \\
        \& \textcolor{fade}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=fade]              
        \end{tikzcd}
        \end{equation*}
        \column{0.49\textwidth}
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \textcolor{source}{C_1} \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[l, "f"',color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]\\
            \& \textcolor{source}{C_3} \arrow[u, "g"', color=source] \arrow[lu, "f \circ g", color=source] \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]
            \end{tikzcd}
        \end{equation*}
        \end{columns}
\end{frame}

\begin{frame}<presentation:1|handout:0>
    \frametitle{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{align*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{align*}
    \end{alertblock}
\end{columns}
\end{frame}

\subsubsection{Natural Transforms}
\begin{frame}<presentation:1|handout:0>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \onslide<|handout:1>{
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}}
\end{frame}

\begin{frame}<presentation:1|handout:0>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:1>{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:1>{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c}", bend left, color=nattran, Rightarrow]}  
            \onslide*<6|handout:0>{\arrow[rr, "\alpha_{c}", color=nattran, Rightarrow]} \& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:1>{\arrow[r, "G"', color=functor,maps to ]}
            \onslide*<2-4|handout:1>{\arrow[l, "F", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:1>{\arrow[dd, "G(f)", color=target, maps to]} \\
            {} 
            \onslide*<4|handout:1>{\arrow[rr, dotted, color=nattran, Rightarrow]}
            \onslide*<5|handout:0>{\arrow[rr, color=nattran, Rightarrow]} \& \& {}                      \\
            \onslide*<2-|handout:1>{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran, Rightarrow]} 
            \onslide*<4-5|handout:0>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran, maps to]}\& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:1>{\arrow[l, "F"', color=functor, maps to]} 
            \onslide*<3-4|handout:1>{\arrow[r, "G", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>
    \frametitle{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            \begin{align*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \\
                 \dfiberc_{\dbasepointc} \subset  \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}

@@

\begin{frame}<presentation:1|handout:1->{}

@@

    \frametitle<4-6|handout:4>{Pullback: data to region of the visualization} 

@@

    \frametitle<7-|handout:5>{Pushforward: visualization to index of data}

@@

            \onslide*<0|handout:2,3,5>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \onslide*<0|handout:5>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<0|handout:5>{\cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}}}  

@@

            \onslide*<0|handout:2,4->{\opensetgc}
            \onslide*<0|handout:3>{\overbrace{\opensetc\times[0,1]^{m}}^{\opensetgc}}
            \onslide*<0|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<0|handout:2,3,5>{\arrow[u, "\sheaf_{\gbasec, \gtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:4>{\arrow[d, dashed, maps to, "\sheaf_{\gbasec, \vindexpullc\dtotalc}"',color=sheaf]} \&  \& 
            \onslide*<0|handout:1,3->{\opensetc}
            \onslide*<0|handout:1,3-4>{\arrow[d, "\sheaf_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:5>{\arrow[u, dashed, maps to, "\sheaf_{\dbasec, \vindexpushc\gtotalc}"', color=sheaf]} \\
            \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}} 

@@

            \onslide*<0|handout:1,3-4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
            \onslide*<0|handout:4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 

@@

    \only<0|handout:1>{% data sheaf

@@

    \only<0|handout:4>{%pulled back data sheaf

@@

    \only<0|handout:2>{% graphic sheaf

@@

    \only<0|handout:5>{%pushed forward sheaf

@@

>>>>

%\documentclass[xcolor={dvipsnames}, handout]{beamer}
\documentclass[xcolor={dvipsnames}]{beamer}
\setbeamertemplate{footline}[frame number]
\setbeamersize{description width=-\labelsep}

@@

%% maybe pull out the middle for now? move the 3 stages down to construction? 
\begin{frame}<presentation:1-|handout:0>{What do visualization libraries do?}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:1>\includegraphics[width=\linewidth]{figures/flow/s2.png}
            \onslide<2|handout:2>\includegraphics[width=\linewidth]{figures/flow/s_vc.png}
            \onslide<3|handout:3>\includegraphics[width=\linewidth]{figures/flow/s_mark.png}
            \onslide<4|handout:4>\includegraphics[width=\linewidth]{figures/flow/s3.png}
        \end{overprint}
    \end{figure}
\end{frame}

@@

\begin{frame}<presentation:1-|handout:0>{Equivariance}
    \begin{description}
        \item[Retinal Variables \& Marks] visual encodings should match properties of the data \cite{bertinSemiologyGraphicsDiagrams2011a}
        \pause
        \item[Graphical Integrity] graphs show \textbf{only} the data\cite{tufteVisualDisplayQuantitative2001}
        \pause 
        \item[Naturalness] easier to understand when properties match\cite{norman_things_smart}
        \pause
        \item[Expressiveness] which structure preserving mappings can a tool implement\cite{mackinlayAutomatingDesignGraphical1986}] 
    \end{description}
\end{frame}

%flip columns
\begin{frame}<presentation:1-|handout:0>{Frameworks for Expressing Visual Equivariance}
    \begin{description}
        \item[linguistically] visualization has syntax, semantics, grammar expresses how to design structure preserving visualizations
        \cite{mackinlayAutomatingDesignGraphical1986,mackinlayAUTOMATICDESIGNGRAPHICAL1987,wilkinsonGrammarGraphics2005}

        \item[algebraically] transformations on data and graphics are equivalent and symmetric \cite{kindlmannAlgebraicProcessVisualization2014}
        \begin{columns}
            \column{.5\textwidth}
            \begin{description}
                \item[D] raw data 
                \item[R] representation (data container) 
                \item[V] visualization
            \end{description}
            \column{.5\textwidth}
            \begin{equation*}
                \begin{tikzcd}[ampersand replacement=\&]
                    D \arrow[d, "\alpha"'] \arrow[r, "r_1"] \& R \arrow[r, "\nu"]  \& V \arrow[d, "\omega"] \\
                    D \arrow[r, "r_2"']                     \& R \arrow[r, "\nu"'] \& V                    
                \end{tikzcd}
                \end{equation*}
        \end{columns} 
    \item[categorically] \textit{understanding} = \textit{read} $\circ$ \textit{render} \cite{vickersUnderstandingVisualizationFormal2013}    
    \end{description}
\end{frame}

@@

\begin{frame}<presentation:1-|handout:1>

@@

    \only<5|handout:1>{

@@

\subsection{Category Theory Language}
\begin{frame}<presentation:1|handout:1>[fragile]{}
    \begin{minted}{python}
        Artist(Data) -> Graphic
    \end{minted}
\end{frame}

\begin{frame}<presentation:1-|handout:1>{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \onslide*<1-|handout:1>{\textcolor{source}{C_1}} 
        \onslide*<3-|handout:1>{\arrow[r, "f", color=source]}
        \onslide*<4-|handout:1>{\arrow[rd, "g\circ f"', color=source]}
        \onslide*<2-|handout:1>{\arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source]} \& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_2}}
        \onslide*<3-|handout:1>{\arrow[d, "g", color=source]} 
        \onslide*<2-|handout:1>{\arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]} \\\& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_3}}
        \onslide*<2-|handout:1>{\arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]}              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}<5-|handout:1>{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}

\begin{frame}<presentation:1-|handout:1>{Opposite Category $\textcolor{source}{\mathcal{C}^{op}}$}
    \begin{columns}
        \column{0.49\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \textcolor{fade}{C_1} \arrow[r, "f", color=fade] \arrow[rd, "g\circ f"', color=fade] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=fade] \& \textcolor{fade}{C_2} \arrow[d, "g", color=fade] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=fade] \\
        \& \textcolor{fade}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=fade]              
        \end{tikzcd}
        \end{equation*}
        \column{0.49\textwidth}
        \onslide*<presentation:2|handout:1>{
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \textcolor{source}{C_1} \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[l, "f"',color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]\\
            \& \textcolor{source}{C_3} \arrow[u, "g"', color=source] \arrow[lu, "f \circ g", color=source] \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]
            \end{tikzcd}
        \end{equation*}
        }
        \end{columns}
\end{frame}

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{align*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{align*}
    \end{alertblock}
\end{columns}
\end{frame}

\subsubsection{Natural Transforms}
\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]                      
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in Ob(\setc)}
            \onslide*<0|handout:1>{\Ob(\setc) \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            \begin{align*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \\
                 \dfiberc_{\dbasepointc} \subset  \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}

@@

\begin{frame}<presentation:1-|handout:1->{}

@@

    \frametitle<4|handout:4>{Pullback: data to region of the visualization} 

@@

    \frametitle<5|handout:5>{Pushforward: visualization to index of data}

@@

            \onslide*<2,3,5|handout:2,3,5>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \onslide*<5|handout:5>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<5|handout:5>{\cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}}}  

@@

            \onslide*<2,4|handout:2,4->{\opensetgc}
            \onslide*<3|handout:3>{\overbrace{\opensetc\times[0,1]^{m}}^{\opensetgc}}
            \onslide*<3-|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<2,3,5|handout:2,3,5>{\arrow[u, "\sheaf_{\gbasec, \gtotalc}", maps to, color=sheaf]}
            \onslide*<4|handout:4>{\arrow[d, dashed, maps to, "\sheaf_{\gbasec, \vindexpullc\dtotalc}"',color=sheaf]} \&  \& 
            \onslide*<1,3-|handout:1,3->{\opensetc}
            \onslide*<1,3-4|handout:1,3-4>{\arrow[d, "\sheaf_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<5|handout:5>{\arrow[u, dashed, maps to, "\sheaf_{\dbasec, \vindexpushc\gtotalc}"', color=sheaf]} \\
            \onslide*<4|handout:4>{\cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}} 

@@

            \onslide*<1,3-4|handout:1,3-4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
            \onslide*<4|handout:4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 

@@

    \only<1|handout:1>{% data sheaf

@@

    \only<4|handout:4>{%pulled back data sheaf

@@

    \only<2|handout:2>{% graphic sheaf

@@

    \only<5|handout:5>{%pushed forward sheaf

@@

\begin{frame}<presentation:1|handout:1->
    \frametitle<presentation:1-|handout:1->{Combining Bundles}
    \frametitle<presentation:2|handout:2>{Transforming Combined Bundles: $\dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \onslide*<presentation:2|handout:2>{\dfunctc_0 \dfuncpullc} \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \onslide*<presentation:1|handout:1>{\arrow[r, "\cdot \otimes \cdot;", phantom]}
                \onslide*<presentation:2|handout:2>{\arrow[r, "\cdots \otimes \cdots", phantom]} 
                \& 
                \onslide*<presentation:2|handout:2>{\dfunctc_i \dfuncpullc} \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \onslide*<presentation:2|handout:2>{\dfunctc_n \dfuncpullc} \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \onslide*<presentation:2|handout:2>{\dfunctc_i \dfuncpullc} \dtotalc_i 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                \onslide*<presentation:2|handout:2>{(\dfunchc=\dfunchc_{i \in [0,n]})}\dbasec 
                \& \& = \&        
                \onslide*<presentation:2|handout:2>{\dfunchc} \dbasec                                               
                \end{tikzcd}                                              
    \end{equation*}
    \onslide*<presentation:1|handout:1>{
        \begin{equation*}
            \prod\limits_{i=0}^{n} \underbrace{Hom(\dbasec,\dtotalc_i)}_{\dsectionc_i} = 
            \underbrace{Hom(\dbasec,  \prod\limits_{i=0}^{n}\dtotalc_i)}_{\dsectionc}
        \end{equation*}}
    \onslide*<presentation:2|handout:2>{
    \begin{equation*}
        \prod\limits_{i=0}^{n} \underbrace{Hom(\dfunchc\dbasec, \dfunctc_i\dfuncpullc \dtotalc_i)}_{\dfuncc_i\dsectionc_i} = 
        \underbrace{Hom(\dfunchc\dbasec,  \prod\limits_{i=0}^{n} \dfunctc_i\dfuncpullc\dtotalc_i)}_{\dfuncc\dsectionc}
    \end{equation*}}
